%
% Template for Doctoral Theses at Uppsala 
% University. The template is based on    
% the layout and typography used for      
% dissertations in the Acta Universitatis 
% Upsaliensis series                      
% Ver 5.2 - 2012-08-08                  
% Latest version available at:            
%   http://ub.uu.se/thesistemplate            
%                                         
% Support: Wolmar Nyberg Akerstrom        
% Thesis Production           
% Uppsala University Library              
% avhandling@ub.uu.se                          
%                                         
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{UUThesisTemplate}

% Package to determine wether XeTeX is used
\usepackage{ifxetex}

\ifxetex
	% XeTeX specific packages and settings
	% Language, diacritics and hyphenation
	\usepackage[babelshorthands]{polyglossia}
	\setmainlanguage{english}
	\setotherlanguages{swedish}

	% Font settings
	\setmainfont{Times New Roman}
	\setromanfont{Times New Roman}
	\setsansfont{Arial}
	\setmonofont{Courier New}
\else
	% Plain LaTeX specific packages and settings
	% Language, diacritics and hyphenation
    % Use English and Swedish languages. 
	\usepackage[swedish,english]{babel} 

	% Font settings
	\usepackage{type1cm}
	\usepackage[latin1]{inputenc}
	\usepackage[T1]{fontenc}
	\usepackage{mathptmx}
	
	% Enable scaling of images on import
	\usepackage{graphicx}
	
	% Mathematical packages
	\usepackage{mathtools}
	\usepackage{amssymb}
	\usepackage{amsfonts}
% 	\usepackage[intlimits]{amsmath}
	\usepackage{bbm}
	\usepackage{braket}
	
	\usepackage{hyperref}
% 	\usepackage{slashed}
% 	\usepackage{psfrag}
% 	\usepackage{wasysym}
	\usepackage{esint}
	
% 	\usepackage[toc,page]{appendix}
\fi


% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Document links and bookmarks
\usepackage{hyperref} 

% Numbering of headings down to the subsection level
\numberingdepth{subsection}

% Including headings down to the subsection level in contents
\contentsdepth{subsection}


% Uncomment to use a custom abstract dummy text
\abstractdummy{
	\begin{abstract}
% 		Please use no more than 300 words and avoid mathematics or complex script.
	The gauge/string duality, a.k.a. the holographic principle is a profound assertion that emerged from string theory. 
	It relates strongly-coupled gauge theories to weakly coupled string theories living in a higher-dimensional curved geometry. 
	Nevertheless, it is a conjecture, and only a few instances of its more concrete form, the AdS/CFT correspondence, are well-understood. 
	The most well-studied example is the duality between N=4 SYM, which is a CFT, and type IIB string theory in AdS5xS5 background. 
	Generalization to less symmetric cases is a must, and the next logical step is to add a mass scale to N=4 SYM, 
	therefore breaking its conformal symmetry and leading to N=2* SYM, the theory we study in this thesis. 
	It is supersymmetric enough to employ the powerful localization method that reduces its partition function to a matrix model. 
	We will see that the mass scale causes non-trivial phase structures in its vacuum configuration, 
	visible in the holographic regime. We will probe them using Wilson loops in different representations of the gauge group. 
	On the other hand, the dual supergravity background was derived by Pilch-Warner, 
	making N=2* theory an explicitly testable non-conformal holographic case, which is a rare example. 
	We will prove that the duality works for the dual observables (string action, D-branes) we managed to compute, 
	even at a quantum-level. 	
	\end{abstract}
}


\begin{document}
\frontmatter
    % Creates the front matter (ti	tle page(s), abstract, list of papers)
    % for either a Comprehensive Summary or a Monograph.
    % Authors of Comprehensive Summaries use this front matter 
    \frontmatterCS 
    % Monograph authors use this front matter 
    %\frontmatterMonograph 
 
   % Optional dedication
%    \dedication{
% 	      He who has a why to live can bear almost any how. \\
%                --- \emph{Friedrich Nietzsche}
%                }
 
    % Environment used to create a list of papers
    \begin{listofpapers}
	\item
X.~Chen-Lin, J.~Gordon, and K.~Zarembo, ``{$ \mathcal{N}={2}^*$
  super-Yang-Mills theory at strong coupling},''
  \href{http://dx.doi.org/10.1007/JHEP11(2014)057}{{\em JHEP} {\bfseries 1411}
  (2014) 057},
\href{http://arxiv.org/abs/1408.6040}{{\ttfamily arXiv:1408.6040 [hep-th]}}.
	\item
X.~Chen-Lin and K.~Zarembo, ``{Higher Rank Wilson Loops in N = 2*
  Super-Yang-Mills Theory},''
  \href{http://dx.doi.org/10.1007/JHEP03(2015)147}{{\em JHEP} {\bfseries 1503}
  (2015) 147},
\href{http://arxiv.org/abs/1502.01942}{{\ttfamily arXiv:1502.01942 [hep-th]}}.	
	\item
X.~Chen-Lin, A.~Dekel, and K.~Zarembo, ``{Holographic Wilson loops in symmetric
  representations in $ \mathcal{N} = {2}^{\ast } $ super-Yang-Mills theory},''
  \href{http://dx.doi.org/10.1007/JHEP02(2016)109}{{\em JHEP} {\bfseries 02}
  (2016) 109},
\href{http://arxiv.org/abs/1512.06420}{{\ttfamily arXiv:1512.06420 [hep-th]}}.	
	\item
X.~Chen-Lin, ``{Symmetric Wilson Loops beyond leading order},''
  \href{http://dx.doi.org/10.21468/SciPostPhys.1.2.013}{{\em SciPost Phys.}
  {\bfseries 1} no.~2, (2016) 013},
\href{http://arxiv.org/abs/1610.02914}{{\ttfamily arXiv:1610.02914 [hep-th]}}.
    	\item 
X.~Chen-Lin, D.~Medina-Rincon, 	K.~Zarembo, ``{Quantum String Test of
  Nonconformal Holography},''
  \href{http://dx.doi.org/10.1007/JHEP04(2017)095}{{\em JHEP} {\bfseries 04}
  (2017) 095},
\href{http://arxiv.org/abs/1702.07954}{{\ttfamily arXiv:1702.07954 [hep-th]}}.
    	\label{apaperlabel}
    \end{listofpapers}
    
    
    \begingroup
        % To adjust the indentation in your table of contents, uncomment and enter the widest numbers for each level
        %  E.g.  \settocnumwidth{widest chapter number}{widest section number}{widest subsection number}...{...}
       %  \settocnumwidth{5}{4}{5}{3}{3}{3}
        \tableofcontents
    \endgroup
    
    % Optional tables
    %\listoftables
    %\listoffigures

\mainmatter
    
    % Include your chapters here.
    
    \input{Chapters/Introduction.tex}
   
   \part{Supersymmetric gauge theories }
     \input{Chapters/Localization.tex}
     \input{Chapters/SYM.tex}
     \input{Chapters/WilsonLoops.tex}
   \part{Gauge/string duality}
     \input{Chapters/supergravity.tex}
     \input{Chapters/AdSCFT.tex}
%      \input{Chapters/Dbranes.tex}
     \input{Chapters/HoloWL.tex}
     
   \input{Chapters/Conclusion}  
   \input{Chapters/SummarySwedish}  
   \input{Chapters/Acknowledgement}  
      
	
\backmatter
    % References
    % No restriction is set to the reference styles
    % Save your references in References.bib
%     \nocite{*} % Remove this for your own citations
    \bibliographystyle{utphys} %halpha has no hyperlink!
    \bibliography{References}


\end{document}\grid
\grid
\grid
\grid
\grid
\grid
